---
title: "Day 2 Assignments"
author: "Paloma Cartwright"
date: "03/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
```

## Derivatives in R

### First Order Univariate Derivates

Find the derivative expression and slope at the indicated value for each of the following

Question A

$f(x) = x^2$ at $x = 3$

```{r}

fx <- expression(x^2)

df_dx <- D(expr = fx, name = "x")

df_dx

x <- 3 

eval(expr = df_dx)

```

Question B

$P(a) = 2(3a+2)^4 - 5$ at $a = 1.2$

```{r}

Pa <- expression(2 * (3 * a + 2) ^ 4 - 5)

dP_da <- D(expr = Pa, name = "a")

dP_da

a <- 1.2 

eval(expr = dP_da)

```

Question C

$g(t) = (-4t)/(t^2+1)^3)$ at $t = 0$

```{r}
gt <- expression((-4 * t)*((t^2 + 1)^-3))

dg_dt <- D(expr = gt, name = "t")
dg_dt

t <- 0

eval(expr = dg_dt)


```

### Higher Order Univariate Derivatives

Find the second derivative with respect to z for $G(z) = 4.6 - 1.9z^3$.

```{r}

Gz <- expression(4.6 - 1.9 * z ^ 3)
#First derivative
dG_dz <- D(expr = Gz, name = "z")
dG_dz
#Second derivative
d2G_dz2 <- D(expr = dG_dz, name = "z")
d2G_dz2

```

### Partial Order Functions

Find all the partials for the following $f(x, y, z) = 2x^2y - 3x + 1 + 4z^4x$

```{r}
f_xyz <- expression(2 * (x ^ 2) * y - 3 * x + 1 + 4 * (z ^ 4) * x)

#Partial derivative for x 
df_dx <- D(expr = f_xyz, name = "x")
df_dx

#Partial derivative for y 
df_dy <- D(expr = f_xyz, name = "y")
df_dy

#Partial derivate for z 
df_dz <- D(expr = f_xyz, name = "z")
df_dz

```

## Plots in R

### Plotting a Function

Plot $f(x) = 2.4e^{-0.05x} sin(x)$

```{r}

fx <- function(x){
  (2.4 * exp(-0.05*x) * sin(x))
}

ggplot(data_frame(x = c(-0.5, 0.5)), aes(x = x)) +
         stat_function(fun = fx)

```


### Plotting Using Penguins Data 

```{r}

ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm)) + 
  geom_point(aes(color = species)) +
  scale_color_manual(values = c("red", "purple", "green"))+ 
  labs(x = "Bill Length (mm)", 
       y = "Bill Width (g)", 
       title = "Relation Between Palmer Penguin Bill Sizes", 
       subtitle = "Data collected by KB Gornat et al. at Palmer Station", 
       color = "Species"
       ) +
  # facet_wrap(~island) + (this made it look gross so I commented it out)
  theme_minimal()


```


```{r}

ggplot(data = penguins, aes(x = species, y = flipper_length_mm)) + 
  geom_jitter(aes(color = species)) +
  scale_color_manual(values = c("red", "purple", "green"))+ 
  labs(x = "Species", 
       y = "Flipper Length (mm)", 
       title = "Relation Between Palmer Penguin Species and Flipper Lengths",
       subtitle = "Data collected by KB Gornat et al. at Palmer Station", 
       color = "Species"
       ) +
  # facet_wrap(~island) + (this made it look gross so I commented it out)
  theme_minimal()

```

